Automatic discovery of cell types and microcircuitry from neural connectomics

### 2014-06-17 docs/paper.tex
build process works
updates to all figs

\documentclass{nature}
\documentclass{article}
\usepackage[english,american]{babel}
\usepackage[backend=biber,style=nature]{biblatex}
\usepackage[disable]{todonotes}
\usepackage{grffile}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{fullpage}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{amsmath}
%\usepackage{subcaption}
%\usepackage{multicol}
\usepackage{csquotes}
\usepackage{pdfpages}
\usepackage{placeins}

@@

\todo{“Anatomist cell type” text}
\todo{Consistent line thickness}
\todo{on adjacency matrix remove text}

@@

\begin{small}
\begin{enumerate}
  \item Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology, Cambridge, Massachusetts
  \item Department of Physical Medicine and Rehabilitation, Northwestern University and Rehabilitation Institute of Chicago, Chicago, Illinois
  \item Department of Physiology, Northwestern University, Chicago, Illinois
  \item Department of Applied Mathematics, Northwestern University, Chicago, Illinois
\end{enumerate}
\end{small}

@@

@@

\being{itemize}
\item \textbf{synthetic}: For synthetic datasets of sizes comparable to our
real data size, do we recover known ground truth information
after running our markov chains for the appropriate amount of time? 
\todo{Add figure}
\item \textbf{autocorrelation} For various summary statistics 
of the latent space, after a certain amount of time 
\todo{add figure}
\end{itemize}

>>>>

\documentclass{nature}
\usepackage[english,american]{babel}
\usepackage[backend=biber,style=nature]{biblatex}
\usepackage[disable]{todonotes}
\usepackage{grffile}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{fullpage}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{amsmath}
%\usepackage{subcaption}
%\usepackage{multicol}
\usepackage{csquotes}
\usepackage{pdfpages}
\usepackage{placeins}

@@

\todo{Consistent line thickness}
\todo{on adjacency matrix remove text}

@@

\begin{small}
\begin{enumerate}
  \item Electrical Engineering and Computer Science, University of California, Berkeley
  \item Department of Physical Medicine and Rehabilitation, Northwestern University and Rehabilitation Institute of Chicago, Chicago, Illinois
  \item Department of Physiology, Northwestern University, Chicago, Illinois
  \item Department of Applied Mathematics, Northwestern University, Chicago, Illinois
\end{enumerate}
\end{small}

@@

\begin{figure}
  \centering 
  \centerline{\includegraphics{comparison.ai}}
  \caption{Comparison of the value of incorporating additional metadata 
for the mouse retina connectome.}
\label{fig:mouseretina_compare}
\end{figure}

\todo{spatial extent comparison}

@@

\begin{itemize}
\item \textbf{synthetic}: For synthetic datasets of sizes comparable to our
real data size, do we recover known ground truth information
after running our markov chains for the appropriate amount of time? 
\todo{Add figure}
\item \textbf{autocorrelation} For various summary statistics 
of the latent space, after a certain amount of time 
\todo{add figure}
\end{itemize}
